Denotational Semantics of Gradual Typing using Synthetic Guarded Domain Theory

### 2024-01-26 paper-new/discussion.tex
discuss Siek-Chen

% Discuss Jeremy Siek's work on graduality in Agda

>>>>

% Discuss Jeremy Siek's work on graduality in Agda
Siek and Chen \cite{siekchen2021} give a proof in Agda of graduality
for an operational semantics. While they do not use the Guarded
Cubical extension, they do use a guarded logic of propositions
shallowly embedded in Agda. Our denotational approach requires full
guarded type theory not just guarded logic. An advantage of the
denotational approach is that it easily validates equational
reasoning, not just graduality, and it is completely independent of
any particular syntax of gradual typing.
